---
title: "Data extraction from bilingual biographies (Chinese-English)"
subtitle: "Based on the Who's Who of American returned students (1917)" 
author: "Cécile Armand"
affiliation: Aix-Marseille University
date: "`r lubridate::today()`"
tags: [who's who directory, biography, bilingual, histtext]  
abstract: |
  This document explains how to use HistText and more generic packages to retrieve and clean the relevant historical information from bilingual biographies, taking the *Who's Who of American returned students* (1917) as a case study.    
  
  <style>
    body {
    text-align: justify}
  </style>
    
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    number_sections: false
    code_folding: show # hide
    fig_caption: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(histtext)
library(tidyverse)
library(quanteda)
library(strex)
library(knitr)
library(kableExtra)
```

# Text preparation

The *Who's Who of American Returned Students* (1917) is part of the "imh collection" of who's who directories generously shared by the Institute of Modern History, Academia Sinica, Taipei. The plain texts of the biographies are stored on a SolR server and can be mined using the [HistText R package](https://bookdown.enpchina.eu/rpackage/HistTextRManual.html).

Load the required packages:
```{r}
library(histtext)
library(tidyverse)
```
<br>
To retrieve the full text, we need to find the title of the book and the name of the target fields: 
```{r}
histtext::list_filter_fields("imh-zh")
histtext::list_possible_filters("imh-zh", "book") 
```
<br>
The book we are interested in is the one titled 游美同學錄 (Youmei tongxuelu). It contains 401 individual entries (biographies). We can now retrieve all biographies, in Chinese and English: 
```{r}
search_imh_zh <- histtext::search_documents_ex('*', corpus = "imh-zh", filter_query = list(book = "游美同學錄"))
search_imh_en <- histtext::search_documents_ex('*', corpus = "imh-en", filter_query = list(book = "游美同學錄"))
```
<br>
Convert row names into ID 
```{r}
search_imh_zh <- tibble::rowid_to_column(search_imh_zh, "ID")
search_imh_en <- tibble::rowid_to_column(search_imh_en, "ID")

search_imh_zh
search_imh_en
```
<br>
Retrieve full text 
```{r}
imh17_zh_docs <- get_documents(search_imh_zh, corpus = "imh-zh", batch_size = 10, verbose = FALSE)
imh17_eng_docs <- get_documents(search_imh_en, corpus = "imh-en", batch_size = 10, verbose = FALSE)
```
<br>
Convert row names into ID again
```{r}
imh17_zh_docs <- tibble::rowid_to_column(imh17_zh_docs, "ID")
imh17_eng_docs <- tibble::rowid_to_column(imh17_eng_docs, "ID")
```
<br> 
Measure length of biographies, based on the number of characters in Chinese, number of words (tokens) in English: 
```{r}
library(quanteda)
imh17_zh_docs <- imh17_zh_docs %>% mutate(length = nchar(Text))
imh17_eng_docs <- imh17_zh_docs %>% mutate(length = ntoken(Text))

imh17_zh_docs
imh17_eng_docs
```
<br>
Save datasets as csv files
```{r}
write.csv(imh17_zh_docs, "imh17_zh_fulltext.csv")
write.csv(imh17_eng_docs, "imh17_eng_fulltext.csv")
```

# Information extraction (Chinese)

First remove extra white space 
```{r}
imh17_zh_clean <- imh17_zh_docs %>% mutate(text_clean = str_squish(Text))
imh17_zh_clean <- imh17_zh_clean %>% mutate(text_clean = str_replace_all(text_clean, " ", ""))
```

## Family data

### Father
Extract father's name
```{r}
family <- imh17_zh_clean %>% mutate(father_name = str_extract(text_clean, "父\\s*(.*?)\\s*。")) 
```
<br>
Extract father's occupation using the structure of the narrative (anything before the current address)
```{r}
family <- family %>% mutate(father_occupation = str_extract(text_clean, "父\\s*(.*?)\\s*本籍住址|本籍通信處|永久通信處|永久住址|家中住址")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"本籍住址")) %>%
  mutate(father_occupation = str_remove_all(father_occupation,"本籍通信處")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"永久通信處")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"永久住址")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"家中住址")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation, father_name))
```
<br>
Remove useless information from father's name/occupation
```{r}
family <- family %>% 
  mutate(father_name = str_remove_all(father_name,"。")) %>%
  mutate(father_name = str_remove_all(father_name,"父")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"。")) %>% 
  mutate(father_occupation = str_remove_all(father_occupation,"已婚"))
```

### Uncle

Extract uncle's name and use the number of character to detect anomalies (names with less or more than 2 characters should be discarded)
```{r}
family <- family %>% mutate(uncle_name = str_extract(text_clean, "叔\\s*(.*?)\\s*。")) %>% 
  mutate(uncle_name = str_remove_all(uncle_name,"。")) %>%
  mutate(uncle_name = str_remove_all(uncle_name,"叔"))  %>% 
  mutate(uncle_nchar = nchar(uncle_name))
```

### Siblings

Elder brother (兄)
```{r}
family <- family %>% mutate(xiong_name = str_extract(text_clean, "兄\\s*(.*?)\\s*。")) 
family <- family %>% mutate(xiong_name = str_remove_all(xiong_name,"。")) %>% # remove punctuation
  mutate(xiong_name = str_remove_all(xiong_name,"兄")) %>% 
  mutate(xiong_nchar = nchar(xiong_name)) # count characters to filter out strings with more than 4 characters
```

Younger brother (弟)
```{r}
family <- family %>% mutate(di_name = str_extract(text_clean, "弟\\s*(.*?)\\s*。")) 
family <- family %>% mutate(di_name = str_remove_all(di_name,"。")) %>% # remove punctuation
  mutate(di_name = str_remove_all(di_name,"弟")) %>% 
  mutate(di_nchar = nchar(di_name))  # count characters to filter out strings with more than 4 characters
```


### Marital status

We rely on pattern matching to retrieve information on their marital status (已婚 = married, 未婚 = unmarried): 
```{r}
married <- c("已婚", "未婚")
married_vec <- paste(married, sep = "", collapse = "|")
family <- family %>% mutate(married = str_extract(text_clean, married_vec)) 
```

### Children

We also rely on pattern matching to extract information on the number of children. After a close examination of the data, we found that the maximum number of sons or daughters was 9. On this basis we create a vector of possible cases (ranging from 1 to 9 sons or daughters). We used the characters "子" and "女" as anchor for sons and daughters, as shown below: 
```{r}
sons <- c("子一", "子二", "子三", "子四", "子五", "子六", "子七", "子八", "子九")
son_vec <- paste(sons, sep = "", collapse = "|")
daugther <- c("女一", "女二", "女三", "女四", "女五", "女六", "女七", "女八", "女九")
daugther_vec <- paste(daugther, sep = "", collapse = "|")
family <- family %>% mutate(sons = str_extract(text_clean, son_vec)) %>% 
  mutate(sons = str_remove_all(sons,"子"))
family <- family %>% mutate(daugthers = str_extract(text_clean, daugther_vec)) %>% 
  mutate(daugthers = str_remove_all(daugthers,"女"))
```
<br>
Inspect last output with all family information:  
```{r}
head(family)
```

## Education

### Source of funding

To retrieve information related to the students' source of funding, we again relied on pattern matching. We first closely read a sample of biographies to identify all possible types of funding. Then we create a vector listing the four possibles cases: 

  * "官費遊美" (guanfei youmei): government sponsored student
  * "公費遊美" (gongfei youmei): other public funding (other than government)
  * "後得半官費" (houdeban guanfei): partial government scholarship
  * "自費遊美" (zifei youmei): self-funded student

```{r}

funding <- c("官費遊美", "公費遊美", "半官費遊美", "自費遊美")
funding_vec <- paste(funding, sep = "", collapse = "|")
family_funding <- family %>% mutate(funding = str_extract(text_clean, funding_vec)) %>% 
  mutate(funding = str_remove_all(funding,"遊美")) 

```

### Year of return

To retrieve then year when the students returned to China, we used the "search_concordance" function included in the histtext package: 
```{r}
search_imh_zh_conc <- histtext::search_concordance_ex('"回國" | "囘國"', 
                                                      corpus = "imh-zh", context_size = 15, 
                                                      filter_query = list(book = "游美同學錄"))

```
<br>
We found the pattern appears once in 366 biographies, twice in 6 of them (the students have been abroad and returned twice), whereas 35 biographies do not contain the pattern (either because the student have not returned, or because another expression was used): 
```{r}
search_imh_zh_conc %>% group_by(DocId) %>% count(sort = TRUE)
```
<br>
Find out who is missing: 
```{r}
setdiff(family$DocId, search_imh_zh_conc$DocId)
```
<br>
Remove white spaces from "before" and "After" 
```{r}

imh_zh_conc <- search_imh_zh_conc %>% mutate(before_clean = str_replace_all(Before, " ", "")) %>% 
  mutate(after_clean = str_replace_all(After, " ", ""))
```
<br>
Clean the field "Before" 
```{r}
imh_zh_conc <- imh_zh_conc %>% mutate(return_date = str_sub(before_clean, - 7, - 1)) %>% 
    mutate(return_date_clean = str_replace_all(return_date, "年。", "年")) %>% 
    mutate(return_date_clean = str_remove(return_date_clean,".*。")) %>% 
    mutate(return_date_clean = str_replace_all(return_date_clean, "</p>", "")) %>% 
    mutate(return_date_clean = str_replace_all(return_date_clean, "p>", "")) %>%
    mutate(return_date_clean = str_replace_all(return_date_clean, "/", "")) %>%
      relocate(return_date_clean, .before = Matched)
```
<br>
Extract date patterns for further cleaning. We use a vectorized list of temporal referentials to be found in the text:  

  * "光緖": Guangxu emperor's reign (1875-1908)
  * "宣統": Xuantong (Pu Yi)'s reign (1909-1911)
  * "民國": Republican calendar (1912-)
  * "是年": this year
  
```{r}
zh_date <- c("民國", "宣統", "光緖", "是年")
zh_date_vec <- paste(zh_date, sep = "", collapse = "|")
imh_zh_conc <- imh_zh_conc %>% mutate(date_zh = str_extract(return_date_clean, zh_date_vec)) %>%
  relocate(date_zh, .before = return_date_clean)
```
<br> 
Clean the field "After"
```{r}
imh_zh_conc <- imh_zh_conc %>% mutate(after_return_clean = str_replace_all(after_clean, "國 。", "")) %>%
  mutate(after_return_clean = str_remove(after_return_clean,".。 任*")) %>%
  mutate(after_return_clean = str_replace_all(after_return_clean,"。 ", "")) %>% 
  mutate(after_return_clean = str_replace_all(after_return_clean, " ", "")) %>% 
  mutate(after_return_clean = str_replace_all(after_return_clean,"。", "")) %>% 
  mutate(after_return_clean = str_replace_all(after_return_clean,"<", "")) %>% 
  mutate(after_return_clean = str_replace_all(after_return_clean,"p>", "")) %>%
  relocate(after_return_clean, .after = Matched)
```
<br>
Extract date patterns for further cleaning
```{r}
imh_zh_conc <- imh_zh_conc %>% mutate(after_date_zh = str_extract(after_return_clean, zh_date_vec))  %>%
  relocate(after_date_zh, .after = after_return_clean)  %>%
  mutate(post_return = str_sub(after_return_clean, 1, 1)) %>% 
  relocate(post_return, .after = after_date_zh) 
```
<br>
Select variables for joining with family and funding data
```{r}

conc_zh_to_join <- imh_zh_conc %>% select(DocId, date_zh, return_date_clean, Matched, after_return_clean, after_date_zh) %>% 
  rename(return_date = return_date_clean, post_return = after_return_clean)

imh_zh_conc_join <- full_join(family_funding, conc_zh_to_join, by = "DocId")  

imh_zh_conc_join

```

## Places

### Address
Extract and clean current address (in 1917)
```{r}

library(strex)

address <- histtext::search_concordance_ex('"本籍住址" | "本籍通信處"|"永久通信處"|"永久住址"|"家中住址"', 
                                              corpus = "imh-zh", context_size = 30, 
                                              filter_query = list(book = "游美同學錄"))

address_clean <- address %>% select(DocId, Matched, After)

address_clean <- address_clean %>% mutate(address = str_before_nth(After, "。", 2)) %>%
  mutate(address = str_replace_all(address,"。", ""))  %>% 
  rename(address_to_clean = After) %>% 
  relocate(address_to_clean, .after = address) %>% 
  mutate(address_to_clean = str_remove_all(address_to_clean,"。")) 

imh_zh_conc_join <- full_join(imh_zh_conc_join, address_clean, by = "DocId")

```
### Ancestry (原籍)

```{r}

ancestry <- histtext::search_concordance_ex('"原籍"', 
                                                   corpus = "imh-zh", context_size = 30, 
                                                   filter_query = list(book = "游美同學錄"))

ancestry_clean <- ancestry %>% select(DocId, After)

ancestry_clean <- ancestry_clean %>% mutate(ancestry = str_before_nth(After, "。", 1)) %>% select(DocId, ancestry)

imh_zh_conc_join <- full_join(imh_zh_conc_join, ancestry_clean, by = "DocId")
```


## Save data

```{r}

write.csv(imh_zh_conc_join, "imh_zh_fulltext_to_clean.csv")

```

# Information extraction (English)
