---
title: "Network Analysis of the Who's Who of American Returned Students (1917)"
author: "Cécile Armand"
affiliation: Aix-Marseille University
date: "`r lubridate::today()`"
tags: [who's who directory, biography, bilingual, histtext]  
abstract: |
  This document introduces various network analyses conducted on the *Who's Who of American returned students* (Tsing Hua, 1917), including kinship networks and affiliation networks.     
  
  <style>
    body {
    text-align: justify}
  </style>
    
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    number_sections: false
    code_folding: show # hide
    fig_caption: true
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(igraph)
library(Places)

```

# Kinship Networks

The first step is to load the edge list (representing kinship ties) and the node list (containing students' and relatives' attributes). For a detailed description of the [kinship data](https://bookdown.enpchina.eu/youmei/Statistics.html#Kinship_ties) and the [method for extracting](https://bookdown.enpchina.eu/youmei/01_DataExtraction.html) it from the directory, please refer to the relevant documentation. 
```{r message = FALSE, warning=FALSE}

# load packages

library(readr)
library(tidyverse)
library(igraph)

# load kinship ties (edge list)

library(readr)
kinship <- read_delim("data/kinship.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)

# load kinship node list (to distinguish biography from relative)

kinship_nodes <- read_csv("data/kinship_nodes.csv")
head(kinship_nodes)

```
## Build the Network
```{r message = FALSE, warning=FALSE}

# create network 

g <- graph_from_data_frame(d=kinship, directed = TRUE, vertices=(kinship_nodes))
g

# components(g)

```
<br>
The kinship network contains 376 nodes and 216 ties, representing 172 family components, with sizes ranging from 2 to 6 members in the case of Shi Zhaoji’s (施肇基) family. 

## Visualize the Network

In the next step, we visualize the kinship network.We use the color and shape of nodes to differentiate between the students who are the subject of a biography (red squares) and the relatives mentioned in their biographies (blue circles). The color of ties represent the different types of relations: 

  * Grey ties represent father-son relations
  * Yellow ties represent uncle-nephew relations
  * Green ties represent siblings 
  * Blue ties represent spouse

```{r message = FALSE, warning=FALSE}

# Index nodes shape on nodes type 
V(g)[kinship_nodes$Type == "ego"]$shape <- "square"
V(g)[kinship_nodes$Type == "relative"]$shape <- "circle"
V(g)[kinship_nodes$Type == "ego"]$color <- "red"
V(g)[kinship_nodes$Type == "relative"]$color <- "light blue"

# Index edge color on relation type 
E(g)[kinship$RelationMain == "Father"]$color <- "grey"
E(g)[kinship$RelationMain == "Uncle"]$color <- "gold"
E(g)[kinship$RelationMain == "Brother"]$color <- "yellowgreen"
E(g)[kinship$RelationMain == "Spouse"]$color <- "light blue"

# plot with igraph 
plot.igraph(g, vertex.size = 3, 
            vertex.label.color = "black", 
            vertex.label.cex = 0.3, 
            edge.width=0.5,
            edge.arrow.size=0, 
            edge.curved=0.1, 
            main="Kinship Network of Early Liumei")

```
<br>
To improve legibility, we will remove dyads and isolated nodes by selecting the largest components (size > 2): 
```{r message = FALSE, warning=FALSE}
# Get components
cl <- components(g)

# Extract membership data 

family_components <- data.frame(cl$membership) %>% 
  rownames_to_column("name") %>%
  rename (comp_no = cl.membership) %>% 
  group_by(comp_no) %>% add_tally() %>%
  rename(size = n) %>% 
  relocate(name, .after = size) 

# join with node attributes 

family_components_attributes <- inner_join(family_components, kinship_nodes)

```
<br>
Remove isolated nodes
```{r message = FALSE, warning=FALSE}

family_filtered <- lapply(seq_along(cl$csize)[cl$csize > 1], function(x) 
  V(g)$name[cl$membership %in% x])

subv <- unlist(family_filtered)
kin1 <- as.data.frame(subv) # convert into dataframe

g1 <- induced.subgraph(graph=g,vids=subv)

# g1 has 371 nodes and 213 ties 

# plot reduced graphs

# index nodes shape/color on nodes type 


plot.igraph(g1, vertex.size = 3, 
            vertex.label.color = "black", 
            vertex.label.cex = 0.3, 
            edge.width=2,
            edge.arrow.size=0, 
            edge.curved=0, 
            main="Kinship Network of Early Liumei (no isolates)")


```
<br>

```{r message = FALSE, warning=FALSE}
# remove dyads 

family_filtered2 <- lapply(seq_along(cl$csize)[cl$csize > 2], function(x) 
  V(g)$name[cl$membership %in% x])

subv2 <- unlist(family_filtered2)
kin2 <- as.data.frame(subv2) # convert into dataframe
write.csv(kin2, "kin2.csv")

g2 <- induced.subgraph(graph=g,vids=subv2)

# g2 has 83 nodes and 64 ties 


plot.igraph(g2, vertex.size = 5, 
            vertex.label.color = "black", 
            vertex.label.cex = 0.5, 
            edge.width=2.5,
            edge.arrow.size=0, 
            edge.curved=0, 
            main="Kinship Network of Early Liuei (cluster > 2)")


```

# Affiliation Networks

## All Affiliations

We upload the affiliation data retrieved using Named Entities Recognition (NER), as described in the [Data Extraction Script](https://bookdown.enpchina.eu/youmei/01_DataExtraction.html).
```{r message = FALSE, warning=FALSE}

# load packages

library(readr)
library(tidyverse)

# load data

library(readr)
affiliation_eng <- read_csv("data/affiliation_eng.csv")


head(affiliation_eng)

```

<br>
The dataset contains a total of 3,431 affiliations retrieved from the 401 English biographies. For each affiliation, the table provides the following information: 

  * DocId: unique identifier of the biography in the "imh" collection  
  * name : the name of the person 
  * Organization: the name of the organization he/she was affiliated to  
  * Position: the timing of the affiliation in the person's life, according to the following typology: PRE = before going to the U.S., US = during his/her studies in the U.S., POST = after his/her return to China), and 
  * the nature of the organization, with two levels of granularity (category, category_main).
  
There is a total of 1,305 unique organizations, with frequency ranging from 1 to 96 (in the case of St John's University). The educational sector represents the largest number (536, 40%), followed by associations (254, 19.5%), and media (newspapers, journals) (108, 8%). The largest number of affiliations refer to their period of studies in the US (1460, 42%) (mostly educational institutions, 810, 55%), followed by their post-return career (1154, 33.6%), their life prior to going to the US (803), and other (non-dated) affiliations. 

```{r message = FALSE, warning=FALSE}

# distribution of affiliations

affiliation_eng %>% group_by(Organization) %>% count(sort = TRUE) # distribution by organization 
affiliation_eng %>% distinct(category_main, Organization) %>% group_by(category_main) %>% count(sort = TRUE) # distribution by category
affiliation_eng %>% group_by(Position) %>% count(sort = TRUE) # distribution by life period 


```

### Create the Network

To build the network, we need to create the edge list (list of links between students and organizations) and the node list (category of node, persons or organizations): 
```{r message = FALSE, warning=FALSE}

# create the edge list 

affiliation_edge <- affiliation_eng %>% 
  mutate(DocName = paste(DocId, name, sep = "_")) %>% # we create a synthetic variable compiling the doc Id with the name, in case of homonyms (wife/husbands)
  select(DocName, Organization, Position)

# create the node list

person_node <- affiliation_edge %>% 
  distinct(DocName) %>% 
  mutate(Type = "Person") %>% 
  mutate(Type2 = "Person") %>% 
  rename(Name = DocName)

org_node <- affiliation_eng %>% 
  distinct(Organization, category_main) %>% 
  mutate(Type = "Organization") %>% 
  rename(Name = Organization, 
         Type2 = category_main) %>% 
  select(Name, Type, Type2)

affiliation_node <- bind_rows(person_node, org_node)

```
<br> 
Next, we create the bipartite network with igraph: 

```{r message = FALSE, warning=FALSE}

library(igraph)

# Creating a network from the edge list
Net <- graph_from_data_frame(affiliation_edge, directed = FALSE)
## Transformation into a 2-mode network
V(Net)$type <- bipartite_mapping(Net)$type
# Projection
projNet <- bipartite_projection(Net, multiplicity = TRUE)
Net1 <- projNet$proj1  # Network of persons
Net2 <- projNet$proj2  # Network of organizations
```

### Visualize the Networks

```{r message = FALSE, warning=FALSE}

# assign color to type of node
V(Net)$shape <- ifelse(V(Net)$Type == "Person", "square","circle")
V(Net)$color <- ifelse(V(Net)$Type == "Person", "tomato","blue")

plot(Net, vertex.size = 3, 
     vertex.color = V(Net)$color, 
      vertex.shape = V(Net)$shape ,
     vertex.label.color = "black", 
     vertex.label.cex = 0.3, 
     main="Early Liumei Affiliation Network")

```

```{r message = FALSE, warning=FALSE}
# remove labels and make size proportionate to degree

layout <- layout_nicely(Net)
  
plot(Net, vertex.size = degree(Net)*0.15, 
     vertex.color = V(Net)$color, 
      vertex.shape = V(Net)$shape ,
     vertex.label = NA, 
     layout = layout, 
     main="Early Liumei Affiliation Network")
```


<br>
Plot projections 
```{r message = FALSE, warning=FALSE}

plot(Net1, vertex.size = 3, 
     vertex.color = "orange", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.3, 
     main="Network of persons linked by organizations")


plot(Net2, vertex.size = 3, 
     vertex.color = "steel blue", 
     vertex.label.color = "black", 
     vertex.label.cex = 0.3, 
     main="Network of organizations linked by persons")

```


## Education
## Employment
## Associative life
